Machine Learning for Predictive Auto-Tuning

### 2011-12-13 paper/draft1.tex
draft1

Figure~\ref{fig:speedup} shows the effectiveness of empirical auto-tuning is in this setting.  Averaging across the range of problem configurations in our study,
implementations discovered by empirical auto-tuning are on average about 50\% (XXX check) faster than the reference implementation.
XXX: recalculate with simpler mean speedup formula.
On the GTX 295 speedups over the reference implementation ranged from XXX to XXX with mean XXX.
On the GTX 480 speedups over the reference implementation ranged from XXX to XXX with mean XXX.
XXX: Consider table for these numbers.
XXX: Put in some timings of mixed \& matched all-stars to show that indeed the reference was a good general baseline, and in fact the auto-tuned models are special-purpose.
\begin{figure}
\centering
\includegraphics[scale=.42]{allstars_mixup_295.pdf}
\caption{Different arguments call for different kernels: each point corresponds to a randomly drawn argument configuration.
The reference speed (horizontal) is completely uncorrelated to the speed of an optimal kernel for an unrelated argument configuration (trials performed on GTX 295).
Out of 100 random confurations, 38 (not shown) could not even be run using a kernel that was auto-tuned for different arguments.
Good performance across a variety of inputs requires {\em input-dependent auto-tuning}.
}
\label{fig:speedup}
\end{figure}

>>>>

Figure~\ref{fig:speedup} shows the effectiveness of empirical auto-tuning is in this setting.  Averaging across the range of problem configurations in our study,
implementations discovered by empirical auto-tuning are on average about 50\% (XXX check) faster than the reference implementation.
XXX: recalculate with simpler mean speedup formula.
On the GTX 295 speedups over the reference implementation ranged from XXX to XXX with mean XXX.
On the GTX 480 speedups over the reference implementation ranged from XXX to XXX with mean XXX.
XXX: Consider table for these numbers.
XXX: Put in some timings of mixed \& matched all-stars to show that indeed the reference was a good general baseline, and in fact the auto-tuned models are special-purpose.
\begin{figure}
\centering
\includegraphics[scale=.42]{allstars_mixup_295.pdf}
\caption{Different arguments call for different kernels:
{\em left} is the average argument-specific empirical auto-tuned performance across 100 random argument configurations,
{\em middle} is the average speed of our reference implementation,
{\em right} is the average speed of kernels auto-tuned for different argument configurations than the one being tested.
For 38/100 random confurations, the kernel auto-tuned for another problem could not even run on the GTX 295 hardware.
These points contributed a speed of 0, bringing down the average much lower than the reference.
Good performance across a variety of inputs requires {\em input-dependent auto-tuning}.
}
\label{fig:speedup}
\end{figure}
